Artin Group Presentations Arising from Cluster Algebras

### 2014-08-06 Presentation/Prob6.tex
Edits to Presentation

\begin{frame}
In constructing the isomorphism between $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
\begin{lemma}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$, and let A$_{\Gamma^{op}}$ be generated by $r_{1}, \dots, r_{n}$. Then the map $$\Delta: s_{i} \rightarrow r_{i}^{-1}$$ defines an isomorphism between A$_{\Gamma}$ and A$_{\Gamma^{op}}.$
\end{lemma}
\end{frame}

\begin{frame}
Now let $A_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$ and let $A_{\Gamma^{\prime}}$ be generated by $u_{1}, \dots, u_{n}$. Consider the map $\phi: A_{\Gamma^{\prime}} \rightarrow A_{\Gamma}$ defined as follows:
$$\phi(u_{i}) = 
\begin{cases}
s_{k}s_{i}s_{k}^{-1} &\text{if there is an arrow from i to k in $\Gamma$} \\
s_{i} &\text{otherwise}
\end{cases}$$

@@

\begin{frame}
Now given the maps $\phi$ and $\Delta$, we are able to prove our theorem. Consider the diagram:
\begin{figure}
\includegraphics[scale = .50]{Comm-Diag.pdf}
\end{figure}
One can check that this diagram commutes, and so we find that the map $\phi$ is actually an isomorphism.
\end{frame}

\section{Affine Dynkin Diagrams}
\begin{frame}
It is natural to ask whether a similar result holds for diagrams that are not of finite type. In particular, we will examine diagrams which are mutation equivalent to affine Dynkin diagrams.
\begin{figure}
\includegraphics[scale = .50]{Affine-Diagrams.pdf}
\caption{Affine Dynkin Diagrams}
\end{figure}
\end{frame}

\begin{frame}
In a paper by Felickson and Tumarkin, the authors obtain a similar result for coxeter groups. For a diagram $\Gamma$ of affine type with n+1 nodes, they define a group W$_{\Gamma}$ generated by elements $s_{1}, \dots, s_{n+1}$ and subject to the following relations:

@@

\begin{frame}
(R3) For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\end{frame}

\begin{frame}
(R4) To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram1.pdf}
\end{figure}
we add the relation $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$.
\end{frame}

\begin{frame}
To a subdiagram of the form 
\begin{figure}
\includegraphics[scale = .50]{Diagram2.pdf}
\end{figure}
we add the relation $(s_{1}s_{2}s_{3}s_{2}s_{1}s_{4}s_{5} \dots s_{n}s_{n+1}s_{n} \dots s_{5}s_{4})^{2} = e$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram3.pdf}
\end{figure}
we add the relations $(s_{2}s_{3}s_{4}s_{1}s_{4}s_{3})^{2} = e$ and $(s_{2}s_{1}s_{4}s_{3}s_{4}s_{1})^{2} = e$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram4.pdf}
\end{figure}
we add the relation $(s_{n+1}s_{1}s_{n+1}s_{2}s_{3} \dots s_{n-1}s_{n}s_{n-1} \dots s_{3}s_{2})^{2} = e$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram5.pdf}
\end{figure}
we add the relations $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$
\end{frame}

@@

\begin{frame}
In their paper, Felickson and Tumarkin show that all of the (R4) relations are necessary for this theorem to be true. For example, consider the mutation of \includegraphics[scale = .30]{Diagram2.pdf} at the vertex 1, which is the diagram
\begin{figure}
\includegraphics[scale = .30]{Diagram6.pdf}
\end{figure}
\end{frame}

\begin{frame}
Let $\Gamma$ be a diagram of affine type on n+1 nodes. Then we define $A_{\Gamma}$ to be the group generated by $s_{1}, \dots, s_{n+1}$ satisfying the relations

@@

\begin{frame}
(T3)  For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram1.pdf}
\end{figure}
we add the relation $(s_{2}s_{1}s_{2}^{-1})s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}(s_{2}s_{1}s_{2}^{-1}).$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram2.pdf}
\end{figure}
we add the relation
$s_{2}(s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})$
\newline $= (s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})s_{2}$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram3.pdf}
\end{figure}
we add the relations $s_{2}s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3} = s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3}s_{2}$ and \\
$s_{2}s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1} = s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1}s_{2}$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram4.pdf}
\end{figure}
we add the relation $s_{1}(s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2}) = (s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2})s_{1}$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram5.pdf}
\end{figure}
we add the relations $s_{2}s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1} = s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$.
\end{frame}

@@

\bibitem{BM}[1] Barot, M. and Marsh, R., Reflection Group Presentations Arising from Cluster Algebras, \emph{Preprint}, arXiv:1112.2300 (2011)
\bibitem{FZ}[2] Fomin, S. and Zelevinsky, A., Cluster Algebras I. Foundations, \emph{J. Amer. Math. Soc.}, \textbf{15} (2002), 497-529.
\bibitem{FZ}[3] Fomin, S. and Zelevinsky, A., Cluster Algebras II. Finite type classification, \emph{Invent. Math.}, \textbf{154} (2003), 63-121.

>>>>

\begin{frame}{Constructing the Isomorphism}
To prove this theorem, our strategy will be to construct homomorphisms so that the following diagram commutes.
\begin{figure}
\includegraphics[scale = .50]{Comm-Diag.pdf}
\end{figure}
Then the map $\phi$ will give us the desired isomorphism.
\end{frame}

\begin{frame}{Constructing the Isomorphism}
We first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
\begin{lemma}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$, and let A$_{\Gamma^{op}}$ be generated by $r_{1}, \dots, r_{n}$. Then the map $$\Delta: s_{i} \rightarrow r_{i}^{-1}$$ defines an isomorphism between A$_{\Gamma}$ and A$_{\Gamma^{op}}.$
\end{lemma}
\end{frame}

\begin{frame}{Constructing the Isomorphism}
Now let $A_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$ and let $A_{\Gamma^{\prime}}$ be generated by $u_{1}, \dots, u_{n}$. Consider the map $\phi: A_{\Gamma^{\prime}} \rightarrow A_{\Gamma}$ defined as follows:
$$\phi(u_{i}) = 
\begin{cases}
s_{k}s_{i}s_{k}^{-1} &\text{if there is an arrow from i to k in $\Gamma$} \\
s_{i} &\text{otherwise}
\end{cases}$$

@@

\begin{frame}{Sketch of Proof of the Main Theorem}
Now consider the diagram:
\begin{figure}
\includegraphics[scale = .50]{Comm-Diag.pdf}
\end{figure}
One can check that this diagram commutes, and so we find that the map $\phi$ is actually an isomorphism, which proves our theorem.
\end{frame}

\section{Affine Dynkin Diagrams}
\begin{frame}{Extending Result to Other Diagrams}
It is natural to ask whether a similar result holds for diagrams that are not of finite type. In particular, we will examine diagrams which are mutation equivalent to affine Dynkin diagrams.
\begin{figure}
\includegraphics[scale = .50]{Affine-Diagrams.pdf}
\caption{Affine Dynkin Diagrams}
\end{figure}
\end{frame}

\begin{frame}{Extending the Barot-Marsh Presentation}
In a paper by Felickson and Tumarkin, the authors obtain a similar result for coxeter groups. For a diagram $\Gamma$ of affine type with n+1 nodes, they define a group W$_{\Gamma}$ generated by elements $s_{1}, \dots, s_{n+1}$ and subject to the following relations:

@@

\begin{frame}{Extending the Barot-Marsh Presentation}
(R3) For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\end{frame}

\begin{frame}{Extending the Barot-Marsh Presentation}
(R4) To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram1.pdf}
\end{figure}
we add the relation $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$.
\end{frame}

\begin{frame}{Extending the Barot-Marsh Presentation}
To a subdiagram of the form 
\begin{figure}
\includegraphics[scale = .50]{Diagram2.pdf}
\end{figure}
we add the relation $(s_{1}s_{2}s_{3}s_{2}s_{1}s_{4}s_{5} \dots s_{n}s_{n+1}s_{n} \dots s_{5}s_{4})^{2} = e$
\end{frame}

\begin{frame}{Extending the Barot-Marsh Presentation}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram3.pdf}
\end{figure}
we add the relations $(s_{2}s_{3}s_{4}s_{1}s_{4}s_{3})^{2} = e$ and $(s_{2}s_{1}s_{4}s_{3}s_{4}s_{1})^{2} = e$.
\end{frame}

\begin{frame}{Extending the Barot-Marsh Presentation}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram4.pdf}
\end{figure}
we add the relation $(s_{n+1}s_{1}s_{n+1}s_{2}s_{3} \dots s_{n-1}s_{n}s_{n-1} \dots s_{3}s_{2})^{2} = e$.
\end{frame}

\begin{frame}{Extending the Barot-Marsh Presentation}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram5.pdf}
\end{figure}
we add the relations $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$
\end{frame}

@@

\begin{frame}{Purpose of (R4) Relations}
In their paper, Felickson and Tumarkin show that all of the (R4) relations are necessary for this theorem to be true. For example, consider the mutation of \includegraphics[scale = .30]{Diagram2.pdf} at the vertex 1, which is the diagram
\begin{figure}
\includegraphics[scale = .30]{Diagram6.pdf}
\end{figure}
\end{frame}

\begin{frame}{Extending our Artin Group Presentations}
Let $\Gamma$ be a diagram of affine type on n+1 nodes. Then we define $A_{\Gamma}$ to be the group generated by $s_{1}, \dots, s_{n+1}$ satisfying the relations

@@

\begin{frame}{Extending our Artin Group Presentations}
(T3)  For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\end{frame}

\begin{frame}{Extending our Artin Group Presentations}
(T4) To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram1.pdf}
\end{figure}
we add the relation $(s_{2}s_{1}s_{2}^{-1})s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}(s_{2}s_{1}s_{2}^{-1}).$
\end{frame}

\begin{frame}{Extending our Artin Group Presentations}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram2.pdf}
\end{figure}
we add the relation
$s_{2}(s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})$
\newline $= (s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})s_{2}$
\end{frame}

\begin{frame}{Extending our Artin Group Presentations}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram3.pdf}
\end{figure}
we add the relations $s_{2}s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3} = s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3}s_{2}$ and \\
$s_{2}s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1} = s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1}s_{2}$.
\end{frame}

\begin{frame}{Extending our Artin Group Presentations}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram4.pdf}
\end{figure}
we add the relation $s_{1}(s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2}) = (s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2})s_{1}$.
\end{frame}

\begin{frame}{Extending our Artin Group Presentations}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram5.pdf}
\end{figure}
we add the relations $s_{2}s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1} = s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$.
\end{frame}

@@

\bibitem{BM}[1] Barot, M. and Marsh, R., Reflection Group Presentations Arising from Cluster Algebras, \emph{Preprint}, arXiv:1112.2300 (2011)
\bibitem{FT}[2] Felikson, A. and Tumarkin, P., Coxeter groups and their quotients arising from cluster algebras, \emph{Preprint}, arXiv{1307.0672} (2013)
\bibitem{FZ}[3] Fomin, S. and Zelevinsky, A., Cluster Algebras I. Foundations, \emph{J. Amer. Math. Soc.}, \textbf{15} (2002), 497-529.
\bibitem{FZ}[4] Fomin, S. and Zelevinsky, A., Cluster Algebras II. Finite type classification, \emph{Invent. Math.}, \textbf{154} (2003), 63-121.
